\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-03-22 docs/paper/paper.tex
add: important-idea

>>>>

\hl{This Idea is very important}
In this work we built a feed forward ANN model that learned the confinement loss given the geometric properties of a SPR-based PCF sensor with fixed pattern and geometrical shape of the cladding air holes. For different types of sensors, Convolutional and Reccurent neural networks can be of great advantage, to discover the spatial insights of variety of patterns and  geometrical shape of the cladding air holes. The latter will be conducted in future work.
